% =====================================================================
%  Uygar Tuna Oflas — Curriculum Vitae
%  Compile with: pdflatex cv.tex
%  Uses only standard packages so it builds on any TeX distribution.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.8cm]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}

% ---- colours --------------------------------------------------------
\definecolor{ink}{HTML}{15181E}
\definecolor{accent}{HTML}{2C44D6}
\definecolor{muted}{HTML}{5C6470}
\definecolor{line}{HTML}{D4D9E0}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% ---- section styling ------------------------------------------------
\titleformat{\section}
  {\color{accent}\large\bfseries\scshape}
  {}{0em}{}[\vspace{2pt}\color{line}\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

\setlist[itemize]{leftmargin=1.1em, itemsep=2pt, topsep=2pt}
\pagestyle{empty}
\renewcommand{\labelitemi}{\color{accent}\textbullet}

% ---- helper: dated entry --------------------------------------------
\newcommand{\entry}[4]{%
  \noindent{\bfseries #1} \hfill {\color{muted}\small #2}\\[-1pt]
  {\color{accent}\small #3} \hfill {\color{muted}\small #4}\par\vspace{2pt}
}

\begin{document}

% =====================================================================
%  Header
% =====================================================================
{\Huge\bfseries\color{ink} Uygar Tuna Oflas}\\[4pt]
{\color{muted}\large Computer Science Student \,\textbullet\, Working-Student Candidate}\\[8pt]
{\small
\href{mailto:tunaoflasoflas@gmail.com}{tunaoflasoflas@gmail.com} \,\textbullet\,
(+90) 546 842 6659 \,\textbullet\,
\href{https://www.linkedin.com/in/uygartunaoflas}{linkedin.com/in/uygartunaoflas} \,\textbullet\,
\href{https://github.com/uygartunaoflas}{github.com/uygartunaoflas}
}
\vspace{4pt}
\noindent{\color{line}\rule{\linewidth}{0.6pt}}

% =====================================================================
%  Profile
% =====================================================================
\section{Profile}
Computer science student with hands-on experience supporting technical events and
group coding projects. I enjoy turning problems into clean, well-structured code,
working in international teams, and learning new tools quickly. Comfortable with
Python, JavaScript and PHP, and currently building a portfolio of small,
well-documented projects.

% =====================================================================
%  Education
% =====================================================================
\section{Education}
\entry{Computer Science}{current}{Gisma University of Applied Sciences --- Germany}{}
\vspace{4pt}
\entry{University studies \& computer club}{2023 -- 2024}{At\i l\i m University --- Ankara, Türkiye}{}

% =====================================================================
%  Experience / Volunteering
% =====================================================================
\section{Experience}
\entry{Event Assistant (Volunteer)}{Sep 2023 -- Dec 2024}{At\i l\i m Computer Club, At\i l\i m University}{Ankara, Türkiye}
\begin{itemize}
  \item Helped organise seminars and workshops on programming, AI and cybersecurity.
  \item Provided technical support during events and helped maintain the club's website and social media.
  \item Took part in group coding projects and student-outreach / digital-literacy efforts.
\end{itemize}

% =====================================================================
%  Selected projects
% =====================================================================
\section{Selected Projects}
\begin{itemize}
  \item \textbf{Knight Path Finder} --- shortest knight route on a chessboard using
        breadth-first search, with an interactive browser demo and Python unit tests. \emph{(Python, JavaScript)}
  \item \textbf{Text Insights CLI} --- command-line tool reporting word frequency and
        readability statistics for a text file. \emph{(Python)}
  \item \textbf{Guestbook API} --- minimal endpoint with input validation and safe
        storage of short messages. \emph{(PHP)}
\end{itemize}

% =====================================================================
%  Skills
% =====================================================================
\section{Skills}
\noindent
\begin{tabularx}{\linewidth}{@{}>{\bfseries\color{ink}}l X@{}}
Programming   & Python, JavaScript, PHP, HTML, CSS \\[3pt]
Tools         & Git \& GitHub, VS Code, LaTeX, Adobe Photoshop, Google Workspace, Microsoft Office \\[3pt]
Strengths     & Analytical \& creative thinking, problem solving, planning, prioritisation, clear communication \\[3pt]
Ways of work  & Adaptable, cooperative, comfortable in international environments \\
\end{tabularx}

% =====================================================================
%  Languages
% =====================================================================
\section{Languages}
\noindent
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Turkish} & Native \\[2pt]
\textbf{English} & B2 (independent user) --- listening, reading, speaking, writing \\[2pt]
\textbf{German}  & A1 (basic user) \\
\end{tabularx}

% =====================================================================
%  Extras
% =====================================================================
\section{Interests \& Other}
\noindent
\begin{tabularx}{\linewidth}{@{}>{\bfseries\color{ink}}l X@{}}
Interests       & Chess, TV \& film, literature, music, visual arts, technology, fishing \\[3pt]
Driving licence & AM, B1, B \\
\end{tabularx}

\end{document}
